Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-09-10 paper/paper.tex
Add results on raw MFCCs

Concatenating the first- and second-order joint scattering coefficients, we obtain a feature vector of dimension $???$ for a sound recording of duration $???$.
Computing nearest neighbors with the standard Euclidean measure gives a $\patk$ of $87.0 \pm 5.8$, where the first value indicates the mean and the second the standard deviation.
As a result, this simple transformation of the original signal results in a representation that lends itself naturally to discriminating timbre.
Note that this result is obtained by simply looking at the raw feature vectors---no learning is performed to adapt the transform towards discriminating timbre.

>>>>

Concatenating the first- and second-order joint scattering coefficients, we obtain a feature vector of dimension $???$ for a sound recording of duration $???$.
Computing nearest neighbors with the standard Euclidean measure gives a $\patk$ of $87.0 \pm 5.8$, where the first value indicates the mean and the second the standard deviation.
As a result, this simple transformation of the original signal results in a representation that lends itself naturally to discriminating timbre.
Note that this result is obtained by simply looking at the raw feature vectors---no learning is performed to adapt the transform towards discriminating timbre.
We contrast this with the results obtained with a baseline MFCC feature vector.
This results in a $\patk$ of $85.1 \pm 6.2$.
We therefore conclude that, although the scattering transform provides a good indication of timbral similarity, using its nearest neighbors based on a standard Euclidan distance does not allow us to properly account for the higher-level time--frequency structure characterized by the second-order coefficients.
